---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BIO 625 HW4: Creating own R package - linearmodels

 <!-- badges: start -->
  [![R-CMD-check](https://github.com/igomez39/linearmodels/workflows/R-CMD-check/badge.svg)](https://github.com/igomez39/linearmodels/actions)
  
  [![codecov](https://codecov.io/gh/igomez39/linearmodels/branch/main/graph/badge.svg)](https://codecov.io/gh/igomez39/linearmodels)
  <!-- badges: end -->
  


## Simple Linear Regression

To use the function `linearModels`. Here we have an example of fitting a  simple linear regression model estimating the miles per gallon of a car based off the weight. Note we are assuming the linear model has an intercept. :
```{r, include=FALSE}
linearModels(mtcars, "wt","mpg")
```



## Multiple Linear Regression

To use the function `linearModels`. Here we have an example of fitting a  multiple linear regression model estimating the miles per gallon of a car based off the weight and number of cylinders of the car. Note: if fitting more than one predictor write predictor names in vector form  :
```{r, include=FALSE}
linearModels(mtcars, c("wt","cyl"),"mpg")
```
