---
title: "linearModels_vignette"
output: html_vignette
vignette: >
  %\vignetteIndexEntry{lineareModels_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{utf8}{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(linearModels)
```



To use the function `linearModels`. Here we have an example of fitting a  simple linear regression model estimating the miles per gallon of a car based off the weight :
```{r setup, include=FALSE}
linearModels(mtcars, "wt","mpg")
```





To use the function `linearModels`. Here we have an example of fitting a  multiple linear regression model estimating the miles per gallon of a car based off the weight and number of cylinders of the car. Note: if fitting more than one predictor write predictor names in vector form  :
```{r setup, include=FALSE}
linearModels(mtcars, c("wt","cyl"),"mpg")
```




```{r}
all.equal(linearModels(mtcars, c("wt","cyl"),"mpg"), lm(mpg ~ wt + cyl, mtcars))
```


```{r}
mark(linearModels(mtcars, c("wt","cyl"),"mpg"))
```

```{r}
mark(lm(mpg ~ wt + cyl, mtcars))
```

