---
title: "linearModel_vignette"
output: html_vignette
vignette: >
  %\vignetteIndexEntry{linearModel_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(linearModels)
library(bench)
```



To use the function `linearModels`. Here we have an example of fitting a  simple linear regression model estimating the miles per gallon of a car based off the weight :
```{r, include=FALSE}
linearModels(mtcars, "wt","mpg")
```





To use the function `linearModels`. Here we have an example of fitting a  multiple linear regression model estimating the miles per gallon of a car based off the weight and number of cylinders of the car. Note: if fitting more than one predictor write predictor names in vector form  :
```{r, include=FALSE}
linearModels(mtcars, c("wt","cyl"),"mpg")
```



Below we are checking the linearModels function for accuracy against the original lm model. 
```{r}
mlr1 <- linearModels(mtcars, c("wt","cyl"),"mpg")
mlr2 <- lm(mpg ~ wt + cyl, mtcars)
all.equal(mlr1[,1], round(mlr2$coefficients,digits = 4))
```


Below we are benchamrking the time linearModels takes to run in comparison to the original lm function.
```{r}
mark(linearModels(mtcars,c("wt","cyl"),"mpg"))
```

```{r}
mark(lm(mpg ~ wt + cyl, mtcars))
```

